method

### 2021-08-25 06_Paper/ER-ED/method.Rmd
added crossref

```{r setup, include = FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(targets)
```

@@

"We report how we determined our sample size, all data exclusions (if any), all manipulations, and all measures in the study" in compliance with the 21-word-solution of open science [@simmons2012]

@@

>>>>

```{r setup, include = FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(targets)
library(readxl)
library(here)
```

@@

"We report how we determined our sample size, all data exclusions (if any), all manipulations, and all measures in the study" in compliance with the 21-word-solution of open science [@Simmons2012]

@@

The ER task followed a block design (see Figure X). Participants were told to actively view neutral and negative pictures (see [2.4. Stimuli](##stimuli)).

```{r stimvalues, echo = FALSE}

stim

```
## 2.4. Stimuli

Pictures used in the paradigm were selected from the Emotional Picture Set (EmoPicS) [@Wessa2010] and the International Affective Picture System (IAPS) [@Lang2008]. The 20 neutral pictures (Valence (V): _M_ $\pm$ _SD_ = 4.81 $\pm$ 0.52; Arousal (A): _M_ $\pm$ _SD_ = 3.00 $\pm$ 0.65)
